Robust Bayesian Analysis of Causal Inference Problems

### 2022-10-28 JASA-template.tex
causal

Let an observational study give us the outcomes $Y=(Y_1$, \dots, $Y_n)$ along with 
corresponding treatment indicators $T=(T_1$, \dots, $T_n)$. Then the
individual causal
effect of the treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
\delta \coloneqq E(Y\mid T=1) - E(Y\mid T=0).
\end{align}
However, we can not observe $(Y_i\mid T_i=1)$ and $(Y_i\mid T_i=0)$
simultaneously for the $i$-th individual. Instead, we can estimate
average causal effect of the treatment $T$ so that
\begin{align}
\hat{\delta} \coloneqq 
\frac{\sum_{i=1}^n(Y_i\mid T_i=1) - (Y_i\mid T_i=0)}{n}.
\end{align}
This relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is
equal to the treatment effect when they remain as the control
\cite{winship99}.

>>>>

Let an observational study give us the outcomes $Y=(Y_1$, \dots, $Y_n)$ along with 
corresponding treatment indicators $T=(T_1$, \dots, $T_n)$. Then the
individual causal
effect of the treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
\delta_i \coloneqq (Y_i\mid T_i=1) - (Y_i\mid T_i=0).
\end{align}
That is, the difference between the outcome when $i$-th subject receives
the treatment and when $i$-th subject remain as a control. Similarly, treatment 
effect of the population is given by the expectation of difference
in outcome between the treatment and controls. 
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - E(Y\mid T=0).
\end{align}

In theory, both of these quantities exist.
However, we can not observe $(Y_i\mid T_i=1)$ and $(Y_i\mid T_i=0)$
simultaneously for the $i$-th individual. Instead, we can estimate
average causal effect of the treatment $T$ by calculating the averaged
outcome of all the subjects those received the treatment and
all the subjects those remained as control.
\begin{align}
\hat{\delta} \coloneqq 
\frac{\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=1) - 
	\sum_{i=1}^n Y_i\cdot\mathbb{I}(T_i=0)}{n}.
\end{align}
However, this relies on an important assumption that the treatment effect
on the $i$-th subject given that they received the treatment is
equal to the treatment effect when they remain as the control
\cite{winship99}.
